Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-09 manuscript/climate_sensitivity_draft.Rmd
update abstract
per Neil's suggestion

### Summary
- As climate change drives increased drought in many forested regions, mechanistic understanding of the factors conferring drought tolerance in trees is increasingly important. The dendrochronological record provides a window through which we can understand how tree size and species’ traits shape growth responses to droughts.

@@

- Tree height and leaf drought tolerance traits influence growth responses during and after drought, as recorded in the tree-ring record spanning historical droughts. As climate change-induced droughts intensify, tall trees with drought-sensitive leaves will be most vulnerable to immediate and longer-term growth reductions.

>>>>

### Summary
- As climate change drives increased drought in many forested regions, mechanistic understanding of the factors conferring drought tolerance in trees is increasingly important. The dendrochronological record provides a window through which we can understand how tree size and traits shape growth responses to droughts.

@@

- The tree-ring record reveals that tree height and leaf drought tolerance traits influenced growth responses during and after significant droughts in the meteorological record. As climate change-induced droughts intensify, tall trees with drought-sensitive leaves will be most vulnerable to immediate and longer-term growth reductions.
